SVG: The Paper

### 2022-04-14 Analysis/index.Rmd
a little tidy up

# item weights pre-computed - see xxxxx.R
a <- readRDS("scratch/qjep_model_weights.rda") %>%
  filter(found != 1) # remove initial selections

@@

>>>>

# item weights pre-computed - see scripts/extract_item_weights_using_model.R
a <- readRDS("scratch/qjep_model_weights.rda") %>%
  filter(found != 1) # remove initial selections

@@

# Shortest Path Analysis

It looks like some of the target selections that our model fails to capture are when participants select a further away target in order to mimimise overall path length. Here we will compare our model's predicted path length against the empirical paths.
